P versus NP

### 2020-01-09 doc/manuscript.tex
Fixed detail
Fixed technical detail

Hartmanis and Mahaney have also shown with their result that if $1NL \subseteq L$ or even $1NL \subset L$, then $L=NL$, because they proved there is a complete problem for both $1NL$ and $NL$ at the same time \cite{HM81}. If this way, if $L \neq NL$, then $L \subset 1NL$ by contraposition \cite{Pap03}. Since we already obtained that $P = NP$ under the assumption that $L \subset 1NL$, therefore if $L \neq NL$, then $P = NP$.
\end{proof}

@@

\begin{proof}
Given a valid instance $(\psi, K)$ for $MAX\oplus2SAT$ when $\psi$ has $m$ clauses, we can create a certificate array $A$ which contains $K$ different natural numbers in ascending order which represents the indexes of the clauses in $\psi$ that we are going to remove from the instance. We read at once the elements of the array $A$ and we reject whether this is not an appropriated certificate: That is when the numbers are not sorted in ascending order, or the array $A$ does not contain exactly $K$ elements, or the array $A$ contains a number that is not between $1$ and $m$. While we read the elements of the array $A$, we remove the clauses from the instance $(\psi, K)$ for $MAX\oplus2SAT$ just creating another instance $\phi$ for $\textit{XOR 2SAT}$ where the Boolean formula $\phi$ does not contain the $K$ different indexed clauses $\psi$ represented by the numbers in $A$. Therefore, we obtain the array $A$ would be valid according to the Theorem \ref{proof} when:
\[(\psi, K) \in MAX\oplus2SAT \textit{ if and only if } \phi \in \textit{XOR 2SAT}.\]
Furthermore, we can make this verification in logarithmic space such that the array $A$ is placed on the special read-once tape, because we read at once the elements in the array $A$ and we assume the clauses in the input $\psi$ are indexed from left to right. Hence, we only need to iterate from the elements of the array $A$ to verify whether the array is an appropriated certificate and also remove the $K$ different clauses from the Boolean formula $\psi$ when we write the final clauses to the output. This logarithmic space verification will be the Algorithm \ref{algorithm1}. We assume whether a value does not exist in the array $A$ into the cell of some position $i$ when $A[i] = \textit{undefined}$. In addition, we reject immediately when the following comparisons:
\[A[i] \leq max \vee A[i] < 1 \vee A[i] > m\]
hold at least into one single binary digit. Note, in the loop $j$ from $min$ to $max - 1$, we do not output any clause when $max - 1 < min$.

@@

\begin{proof}
Given a Boolean formula $\phi$ in $3CNF$ with $n$ variables and $m$ clauses, we can create a disqualification array $A$ which contains $m$ positive integers between $1$ and $3$ which represents the literals of the clauses in $\phi$ which appear from left to right. We read at once the elements of the array $A$ and we reject whether this is not an appropriated disqualification: That is when the array $A$ does not contain exactly $m$ elements, or the array $A$ contains a number that is not between $1$ and $3$. While we read the elements of the array $A$, we select from the clauses $\phi$ the literals such that these ones occupy the position that represents the number between $1$ and $3$, that is the first, second or third place within the clause from left to right. In this way, we output the selected literals that are represented by a positive or negative (in case of a negated variable) integer just creating another instance $C$ for $\textit{SUM--ZERO}$ where the collection $C$ contains those integers which are the selected literals for each clause in $\phi$. Therefore, we obtain that all the appropriated array $A$ would be valid according to the Theorem \ref{demonstration} when:
\[\phi \in 3UNSAT \textit{ if and only if } C \in \textit{SUM--ZERO}\]
since we assume the positive and negated literals of some variable in the input $\phi$ correspond to a positive integer and its negative value. Furthermore, we can make this disqualification in logarithmic space such that the array $A$ is placed on the special read-once tape, because we read at once the elements in the array $A$. Hence, we only need to iterate from the elements of the array $A$ to verify whether the array is an appropriated disqualification and pick the $m$ literals from the Boolean formula $\phi$ when we write the final integers that represent these literals to the output. This logarithmic space disqualification will be the Algorithm \ref{algorithm2}. We assume whether a value does not exist in the array $A$ into the cell of some position $i$ when $A[i] = \textit{undefined}$. In addition, we reject immediately when the following comparisons:
\[A[i] < 1 \vee A[i] > 3\]
hold at least into one single binary digit. Note, that every possible literal in $\phi$ could have a representation by an integer between $-3 \times m$ and $3 \times m$ with the exception of $0$, where $m$ is the cardinality of the collection $C$. In this way, we guarantee the output collection $C$ is an appropriated instance of $\textit{SUM--ZERO}$ just filling with zeroes to the left the elements with bit-length lesser than $|3 \times m|$ where $|\ldots|$ is the bit-length function.

>>>>

Hartmanis and Mahaney have also shown with their result that if $1NL \subseteq L$ or even $1NL \subset L$, then $L=NL$, because they proved there is a complete problem for both $1NL$ and $NL$ at the same time \cite{HM81}. In this way, if $L \neq NL$, then $L \subset 1NL$ by contraposition \cite{Pap03}. Since we already obtained that $P = NP$ under the assumption that $L \subset 1NL$, therefore if $L \neq NL$, then $P = NP$.
\end{proof}

@@

\begin{proof}
Given a valid instance $(\psi, K)$ for $MAX\oplus2SAT$ when $\psi$ has $m$ clauses, we can create a certificate array $A$ which contains $K$ different natural numbers in ascending order which represents the indexes of the clauses in $\psi$ that we are going to remove from the instance. We read at once the elements of the array $A$ and we reject whether this is not an appropriated certificate: That is when the numbers are not sorted in ascending order, or the array $A$ does not contain exactly $K$ elements, or the array $A$ contains a number that is not between $1$ and $m$. While we read the elements of the array $A$, we remove the clauses from the instance $(\psi, K)$ for $MAX\oplus2SAT$ just creating another instance $\phi$ for $\textit{XOR 2SAT}$ where the Boolean formula $\phi$ does not contain the $K$ different indexed clauses $\psi$ represented by the numbers in $A$. Therefore, we obtain the array $A$ would be valid according to the Theorem \ref{proof} when:
\[(\psi, K) \in MAX\oplus2SAT \textit{ if and only if } (\exists \textit{ array } A \textit{ such that } \phi \in \textit{XOR 2SAT}).\]
Furthermore, we can make this verification in logarithmic space such that the array $A$ is placed on the special read-once tape, because we read at once the elements in the array $A$ and we assume the clauses in the input $\psi$ are indexed from left to right. Hence, we only need to iterate from the elements of the array $A$ to verify whether the array is an appropriated certificate and also remove the $K$ different clauses from the Boolean formula $\psi$ when we write the final clauses to the output. This logarithmic space verification will be the Algorithm \ref{algorithm1}. We assume whether a value does not exist in the array $A$ into the cell of some position $i$ when $A[i] = \textit{undefined}$. In addition, we reject immediately when the following comparisons:
\[A[i] \leq max \vee A[i] < 1 \vee A[i] > m\]
hold at least into one single binary digit. Note, in the loop $j$ from $min$ to $max - 1$, we do not output any clause when $max - 1 < min$.

@@

\begin{proof}
Given a Boolean formula $\phi$ in $3CNF$ with $n$ variables and $m$ clauses, we can create a disqualification array $A$ which contains $m$ positive integers between $1$ and $3$ which represents the literals of the clauses in $\phi$ which appear from left to right. We read at once the elements of the array $A$ and we reject whether this is not an appropriated disqualification: That is when the array $A$ does not contain exactly $m$ elements, or the array $A$ contains a number that is not between $1$ and $3$. While we read the elements of the array $A$, we select from the clauses $\phi$ the literals such that these ones occupy the position that represents the number between $1$ and $3$, that is the first, second or third place within the clause from left to right. In this way, we output the selected literals that are represented by a positive or negative (in case of a negated variable) integer just creating another instance $C$ for $\textit{SUM--ZERO}$ where the collection $C$ contains those integers which are the selected literals for each clause in $\phi$. Therefore, we obtain that all the appropriated array $A$ would be valid according to the Theorem \ref{demonstration} when:
\[\phi \in 3UNSAT \textit{ if and only if } (\forall \textit{ appropriated array } A \textit{ such that } C \in \textit{SUM--ZERO})\]
since we assume the positive and negated literals of some variable in the input $\phi$ correspond to a positive integer and its negative value. Furthermore, we can make this disqualification in logarithmic space such that the array $A$ is placed on the special read-once tape, because we read at once the elements in the array $A$. Hence, we only need to iterate from the elements of the array $A$ to verify whether the array is an appropriated disqualification and pick the $m$ literals from the Boolean formula $\phi$ when we write the final integers that represent these literals to the output. This logarithmic space disqualification will be the Algorithm \ref{algorithm2}. We assume whether a value does not exist in the array $A$ into the cell of some position $i$ when $A[i] = \textit{undefined}$. In addition, we reject immediately when the following comparisons:
\[A[i] < 1 \vee A[i] > 3\]
hold at least into one single binary digit. Note, that every possible literal in $\phi$ could have a representation by an integer between $-3 \times m$ and $3 \times m$ with the exception of $0$, where $m$ is the cardinality of the collection $C$. In this way, we guarantee the output collection $C$ is an appropriated instance of $\textit{SUM--ZERO}$ just filling with zeroes to the left the elements with bit-length lesser than $|3 \times m|$ where $|\ldots|$ is the bit-length function.
